---
title: "association rules"
author: "Xiang Gao"
date: "2018/1/8"
output: html_document
---

This code is showing how to use R to implement association rules, which is used to find frequent itemsets. I came across this concept when reading the book data minining. concepts and techniques. I search for tutorials and find out this one
https://datascienceplus.com/implementing-apriori-algorithm-in-r/

First, I will follow this tutorial, then I would like to implement it on the kaggle ecommerce dataset.

```{r}
df_groceries <- read.csv('Groceries_dataset.csv')
df_groceries
```
```{r}
df_sorted <- df_groceries[order(df_groceries$Member_number),]
df_sorted$Member_number <- as.numeric(df_sorted$Member_number)
df_sorted
```


```{r}
if(sessionInfo()['basePkgs']=="dplyr"|sessionInfo()['otherPkgs']=="dplyr"){detach(package:dplyr, unload=TRUE)
}
library('plyr')

```
Put all items in the itemDescription(seperated by comma) based on same receipt number and date

```{r}
df_itemList <- ddply(df_groceries,c('Member_number','Date'),
                     function(df1)paste(df1$itemDescription,
                                        collapse = ','))
df_itemList
```

Delete member numbers and date
```{r}
df_itemList$Member_number <- NULL
df_itemList$Date <- NULL
colnames(df_itemList) <- 'itemlist'
```
write to csv, transaction id should be automatically attached by make the row.names=TRUE

```{r}
write.csv(df_itemList,'ItemList.csv',quote = F, row.names = T)
```

Find relationships among items, Apriori find these relations
```{r}
install.packages('arules',dependencies = T)
```

```{r}
library(arules)
```

```{r}
txn=read.transactions(file='ItemList.csv',rm.duplicates = FALSE,
                      format='basket',sep=',',cols=1)
```

```{r}
txn@itemInfo$labels <- gsub("\"","",txn@itemInfo$labels)
```

Run aprior by specifying support and confidence
```{r}
basket_rules <- apriori(txn,parameter = list(sup=0.001,conf=0.01,
                                             target='rules'))
```

```{r}
if(sessionInfo()['basePkgs']=="tm" | sessionInfo()['otherPkgs']=="tm"){
        detach(package:tm, unload=TRUE)
}
inspect(basket_rules)
```


```{r}
df_basket <- as(basket_rules,'data.frame')
df_basket
```
```{r}
library(arulesViz)
plot(basket_rules)
plot(basket_rules, method = "grouped", control = list(k = 5))
plot(basket_rules, method="graph", control=list(type="items"))
#plot(basket_rules, method="paracoord",  control=list(alpha=.5, reorder=TRUE))
plot(basket_rules,measure=c("support","lift"),shading="confidence",interactive=T)
```

```{r}
itemFrequencyPlot(txn,topN =5)
```

